---
title: "Reliability of the Emotional Dot Probe Task in Study 2"
---

**STUDY 2: The goals of this file is to (1) use the additional data collected in Study 2 to analyze the reliability of the 8 versions of the Threat Dot Probe Task that showed significantly nonzero split-half reliability in Study 1, and (2) whether reliability is higher among participants with higher anxiety levels. **  

```{r, set-up, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
library(ggpmisc)
library(spearmanCI)
# define colors we use for visualization
colors <- c("#0C7BDC", "#FFC20A", "#7D2F39")

# GAD7
# 0–4: minimal anxiety 
# 5–9: mild anxiety
# 10–14: moderate anxiety 
# 15–21: severe anxiety
# >=10 is clinical cutoff

# Load processed data
# naming convention: s2 - study 2
# Outcome/person level data (one row per participant)
s2.all.outcomes <- read_csv("data/study2/openData_study2_outcomes_032623.csv")
# Trial level data (48 test trials per participant) -> to calculate split half correlation and reliability
s2.all.trials <- read_csv("data/study2/openData_study2_trials_032623.csv")
```


# 1. Quality Control
After excluding participants whose results did not pass data quality control filters (N = 7 with accuracy < 60% or median RTc < 300 ms), the total sample was 1840 with between 202 to 246 participants completing each version. 

```{r quality-control}
# Exclude participants with medRTc < 300 ms or accuracy < 60%
s2.outcomes <- s2.all.outcomes %>%
  filter(all_accuracy >= 0.6 & all_medRTc >= 300)
s2.excluded.id <- s2.all.outcomes[s2.all.outcomes$all_accuracy < 0.6 | s2.all.outcomes$all_medRTc < 300,]$id

# Total N included in analysis = 1840
nrow(s2.outcomes) 
# N excluded = 7
nrow(s2.all.outcomes) - nrow(s2.outcomes)

# Minimum and maximum N for each test version, test_id 14: N = 202, test_id 19: N = 246
s2.outcomes %>% 
  group_by(test_id) %>% 
  summarise(n = n()) %>% 
  arrange(n) %>%
  filter(row_number() == 1 | row_number() == n())
```

```{r process-trial-data, include = FALSE}
# condition 1: Threat congruent trials
# condition 2: Threat incongruent trials
# condition 3: Both threat trials
# condition 4: Both neutral trials
s2.parsed.trials <- s2.all.trials %>%
  # exclude participants who failed quality control criteria
  filter(!(id %in% s2.excluded.id) & condition != "practice") %>%
  mutate(rt = as.numeric(rt),
         correct = as.numeric(correct)) %>%
  group_by(id) %>%
  mutate(
    # number the trials (mixed among all conditions) 
    trial.all.cond = row_number(), 
    # label whether each trial is an odd (1) or even (2) trial (mixed among all conditions)
    half.all.cond = ifelse(trial.all.cond %% 2 == 1, 1, 2)) %>%
  group_by(id, condition) %>%
  mutate(
    # number the trials (within each condition)
    trial.by.cond = row_number(),
    # label whether each trial is an odd (1) or even (2) trial (within each condition)
    half.by.cond = ifelse(trial.by.cond %% 2 == 1, 1, 2))
  
# Calculate MEDIAN RT for odd and even trials (mixed among all conditions)
s2.half.med.rt.all.cond <- s2.parsed.trials %>%
  group_by(id, half.all.cond) %>%
  summarise(half.med.rt.all = median(rt)) %>%
  pivot_wider(names_from = half.all.cond, names_glue = "half.{half.all.cond}.rt", values_from = half.med.rt.all)

# Calculate MEAN accuracy for odd and even trials (mixed among all conditions)
s2.half.mean.acc.all.cond <- s2.parsed.trials %>%
  group_by(id, half.all.cond) %>%
  summarise(half.mean.acc.all = mean(correct)) %>%
  pivot_wider(names_from = half.all.cond, names_glue = "half.{half.all.cond}.acc", values_from = half.mean.acc.all)

s2.half.rt.acc.all.cond <- merge(s2.half.med.rt.all.cond, s2.half.mean.acc.all.cond, by = "id")

# Calculate MEDIAN RT for odd and even trials (within each condition)
s2.half.med.rt.by.cond <- s2.parsed.trials %>%
  group_by(id, condition, half.by.cond) %>%
  summarise(half.med.rt.by.cond = median(rt)) %>%
  pivot_wider(names_from = c(condition, half.by.cond), 
              names_glue = "cond{condition}.{half.by.cond}.rt", 
              values_from = half.med.rt.by.cond) %>%
  # Calculate the differences in median RT
  mutate(TC.TIC.1.rt = cond1.1.rt - cond2.1.rt,
         TC.TIC.2.rt = cond1.2.rt - cond2.2.rt,
         TC.TT.1.rt = cond1.1.rt - cond3.1.rt,
         TC.TT.2.rt = cond1.2.rt - cond3.2.rt,
         TC.NN.1.rt = cond1.1.rt - cond4.1.rt,
         TC.NN.2.rt = cond1.2.rt - cond4.2.rt)

# Calculate MEAN accuracy for odd and even trials (within each condition)
s2.half.mean.acc.by.cond <- s2.parsed.trials %>%
  group_by(id, condition, half.by.cond) %>%
  summarise(half.mean.rt.by.cond = mean(correct)) %>%
  pivot_wider(names_from = c(condition, half.by.cond), 
              names_glue = "cond{condition}.{half.by.cond}.acc", 
              values_from = half.mean.rt.by.cond) %>%
  # Calculate the differences in mean accuracy
  mutate(TC.TIC.1.acc = cond1.1.acc - cond2.1.acc,
         TC.TIC.2.acc = cond1.2.acc - cond2.2.acc,
         TC.TT.1.acc = cond1.1.acc - cond3.1.acc,
         TC.TT.2.acc = cond1.2.acc - cond3.2.acc,
         TC.NN.1.acc = cond1.1.acc - cond4.1.acc,
         TC.NN.2.acc = cond1.2.acc - cond4.2.acc)

s2.half.rt.acc.by.cond <- merge(s2.half.med.rt.by.cond, s2.half.mean.acc.by.cond, by = "id")

# Merge them into 1 df for convenience
s2.half.stats <- merge(s2.half.rt.acc.all.cond, s2.half.rt.acc.by.cond, by = "id")

s2.pt.info <- s2.outcomes %>% select(id, test_id, soa, imageType, orient, cond_num, gad7, bhs, gad7_2lvl, gad7_4lvl, bhs_4lvl, bhs_10lvl, bhs_4lvl_high, bhs_10lvl_high)
s2.half.stats <- merge(s2.pt.info, s2.half.stats, by = "id")
```


```{r df-by-anxiety}
# Separate outcome data by GAD level
s2.outcomes.gad.SEVERE <- s2.outcomes %>%
  filter(gad7_2lvl == "high")

# Separate outcome data by BHS level
s2.outcomes.bhs.topQuartile <- s2.outcomes %>%
  filter(bhs_4lvl_high == "high")
s2.outcomes.bhs.topDecile <- s2.outcomes %>%
  filter(bhs_10lvl_high == "high")

# Separate trial level data by GAD level
s2.half.gad.SEVERE <- s2.half.stats %>%
    filter(gad7_2lvl == "high")

# Separate outcome data by BHS level
s2.half.bhs.topQuartile <- s2.half.stats %>%
  filter(bhs_4lvl_high == "high")
s2.half.bhs.topDecile <- s2.half.stats %>%
  filter(bhs_10lvl_high == "high")
```


```{r version-parameters}
s2.v.params <- s2.outcomes %>%
  group_by(test_id) %>%
  filter(row_number() == 1) %>%
  select(test_id, soa, imageType, orient, cond_num)
```

```{r correlation-by-version}
# ---- PEARSON -----
# Split half PEARSON Correlation of threat facilitation RT scores, by version
s2.rt.pearson <- s2.half.stats %>%
  group_by(test_id) %>%
  summarise(
    n.rt.pearson = n(),
    r.rt.pearson = cor(TC.TIC.1.rt, TC.TIC.2.rt),
    r.rt.pearson.lower = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[1], 2),
    r.rt.pearson.upper = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[2], 2),
    rho.rt.pearson = ifelse(r.rt.pearson > 0, (2*r.rt.pearson)/(1+r.rt.pearson), 0), 
    rho.rt.pearson.lower = round(ifelse(r.rt.pearson.lower > 0, (2*r.rt.pearson.lower)/(1+r.rt.pearson.lower), 0), 2),
    rho.rt.pearson.upper = round(ifelse(r.rt.pearson.upper > 0, (2*r.rt.pearson.upper)/(1+r.rt.pearson.upper), 0), 2),
    p.rt.pearson = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$p.value, 4),
    p.rt.pearson.star = ifelse(p.rt.pearson < .001, "***",
                        ifelse(p.rt.pearson < .01, "** ",
                        ifelse(p.rt.pearson < .05, "*  ", "   "))))

# Split half PEARSON Correlation of threat facilitation ACCURACY scores, by version
s2.acc.pearson <- s2.half.stats %>%
  group_by(test_id) %>%
  summarise(
    n.acc.pearson = n(),
    r.acc.pearson = round(cor(TC.TIC.1.acc, TC.TIC.2.acc), 2),
    r.acc.pearson.lower = round(cor.test(TC.TIC.1.acc, TC.TIC.2.acc)$conf.int[1], 2),
    r.acc.pearson.upper = round(cor.test(TC.TIC.1.acc, TC.TIC.2.acc)$conf.int[2], 2),
    rho.acc.pearson = round(ifelse(r.acc.pearson > 0, (2*r.acc.pearson)/(1+r.acc.pearson), 0), 2),
    rho.acc.pearson.lower = round(ifelse(r.acc.pearson.lower > 0, (2*r.acc.pearson.lower)/(1+r.acc.pearson.lower), 0), 2),
    rho.acc.pearson.upper = round(ifelse(r.acc.pearson.upper > 0, (2*r.acc.pearson.upper)/(1+r.acc.pearson.upper), 0), 2),
    p.acc.pearson = round(cor.test(TC.TIC.1.acc, TC.TIC.2.acc)$p.value, 4),
    p.acc.pearson.star = ifelse(p.acc.pearson < .001, "***",
                         ifelse(p.acc.pearson < .01, "** ",
                         ifelse(p.acc.pearson < .05, "*  ", "   "))))


# --- SPEARMAN ------- 

# Split half SPEARMAN Correlation of threat facilitation RT scores, for versions with sig Pearson correlation
s2.rt.sig.test_ids <- s2.rt.pearson[s2.rt.pearson$p.rt.pearson < .05 & s2.rt.pearson$r.rt.pearson > 0,]$test_id
s2.rt.spearman <- data.frame(
  test_id = 1:36,
  r.rt.spearman = NA, 
  r.rt.spearman.lower = NA, 
  r.rt.spearman.upper = NA,
  p.rt.spearman = NA
)
for (i in s2.rt.sig.test_ids) {
  s2.rt.spearman[i, 2] <- round(cor.test(s2.half.stats[s2.half.stats$test_id == i,]$TC.TIC.1.rt,
                s2.half.stats[s2.half.stats$test_id == i,]$TC.TIC.2.rt, method = "spearman")$estimate, 2)
  s2.rt.spearman[i, 5] <- round(cor.test(s2.half.stats[s2.half.stats$test_id == i,]$TC.TIC.1.rt,
                s2.half.stats[s2.half.stats$test_id == i,]$TC.TIC.2.rt, method = "spearman")$p.value, 4)
}

# Split half SPEARMAN Correlation of threat facilitation ACCURACY scores, for versions with sig Pearson correlation
s2.acc.sig.test_ids <- s2.acc.pearson[s2.acc.pearson$p.acc.pearson < .05 & s2.acc.pearson$r.acc.pearson > 0,]$test_id
s2.acc.spearman <- data.frame(
  test_id = 1:36,
  r.acc.spearman = NA,
  r.acc.spearman.lower = NA, 
  r.acc.spearman.upper = NA,
  p.acc.spearman = NA
)
for (i in s2.acc.sig.test_ids) {
  s2.acc.spearman[i, 2] <- round(cor.test(s2.half.stats[s2.half.stats$test_id == i,]$TC.TIC.1.acc,
                s2.half.stats[s2.half.stats$test_id == i,]$TC.TIC.2.acc, method = "spearman")$estimate, 2)
  s2.acc.spearman[i, 5] <- round(cor.test(s2.half.stats[s2.half.stats$test_id == i,]$TC.TIC.1.acc,
                s2.half.stats[s2.half.stats$test_id == i,]$TC.TIC.2.acc, method = "spearman")$p.value, 4)
}

# Split half SPEARMAN RT CI 
# don't know how to store the outcome of spearmanCI into a table. So I'm manually adding them to the spearman table
# spearmanCI(s2.half.stats[s2.half.stats$test_id == 1,]$TC.TIC.1.rt,
#            s2.half.stats[s2.half.stats$test_id == 1,]$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # rho's CI [-0.121, 0.168]
# spearmanCI(s2.half.stats[s2.half.stats$test_id == 11,]$TC.TIC.1.rt,
#            s2.half.stats[s2.half.stats$test_id == 11,]$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # rho's CI [-0.009, 0.275]
# spearmanCI(s2.half.stats[s2.half.stats$test_id == 12,]$TC.TIC.1.rt,
#            s2.half.stats[s2.half.stats$test_id == 12,]$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # rho's CI [-0.048, 0.231]
# spearmanCI(s2.half.stats[s2.half.stats$test_id == 18,]$TC.TIC.1.rt,
#            s2.half.stats[s2.half.stats$test_id == 18,]$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # rho's CI [-0.036, 0.257]
s2.rt.spearman[1, 3] <- -0.121
s2.rt.spearman[1, 4] <- 0.168
s2.rt.spearman[11, 3] <- -0.009
s2.rt.spearman[11, 4] <- 0.275
s2.rt.spearman[12, 3] <- -0.048
s2.rt.spearman[12, 4] <- 0.231
s2.rt.spearman[18, 3] <- -0.036
s2.rt.spearman[18, 4] <- 0.257
# Calculate rho's CI for the Spearman correlation of TF RT scores
s2.rt.spearman <- s2.rt.spearman %>%
  mutate(
    rho.rt.spearman = round(ifelse(r.rt.spearman > 0, (2*r.rt.spearman)/(1+r.rt.spearman), 0), 2),
    rho.rt.spearman.lower = round(ifelse(r.rt.spearman.lower > 0, (2*r.rt.spearman.lower)/(1+r.rt.spearman.lower), 0), 2),
    rho.rt.spearman.upper = round(ifelse(r.rt.spearman.upper > 0, (2*r.rt.spearman.upper)/(1+r.rt.spearman.upper), 0), 2),
  )

versions <- c(1,10,11,12,14,15,18,19)
s2.rt.spearman <- s2.rt.spearman %>%
  filter(test_id %in% versions)


# Split half SPEARMAN Accuracy CI 
spearmanCI(s2.half.stats[s2.half.stats$test_id == 14,]$TC.TIC.1.acc,
           s2.half.stats[s2.half.stats$test_id == 14,]$TC.TIC.2.acc, level = 0.95, method = "Euclidean", plot = FALSE) # r's CI [-0.023, 0.416]
spearmanCI(s2.half.stats[s2.half.stats$test_id == 19,]$TC.TIC.1.acc,
           s2.half.stats[s2.half.stats$test_id == 19,]$TC.TIC.2.acc, level = 0.95, method = "Euclidean", plot = FALSE) # r's CI [0.036, 0.331]
s2.acc.spearman[14, 3] <- -0.023
s2.acc.spearman[14, 4] <- 0.416
s2.acc.spearman[19, 3] <- 0.036
s2.acc.spearman[19, 4] <- 0.331
# Calculate rho's CI for the Spearman correlation of TF accuracy scores
s2.acc.spearman <- s2.acc.spearman %>%
  mutate(
    rho.acc.spearman = round(ifelse(r.acc.spearman > 0, (2*r.acc.spearman)/(1+r.acc.spearman), 0), 2),
    rho.acc.spearman.lower = round(ifelse(r.acc.spearman.lower > 0, (2*r.acc.spearman.lower)/(1+r.acc.spearman.lower), 0), 2),
    rho.acc.spearman.upper = round(ifelse(r.acc.spearman.upper > 0, (2*r.acc.spearman.upper)/(1+r.acc.spearman.upper), 0), 2),
  )
s2.acc.spearman <- s2.acc.spearman %>%
  filter(test_id %in% versions)
```


# 2. Descriptives and Demographics for the Whole Sample

## 2.1 Demographics 

Across the whole sample, the average age was 36.07 (SD = 15.34); 53.78% of participants identified as female, 42.34% identified as male, and 3.86% identified as nonbinary or gender queer. Of the total sample, 78.14% identified as European or White, 16.63% identified as Asian, 5.61% identified as African or Black, 2.97% identified as American Indian or Alaska Native, 0.84% identified as Native Hawaiian or Pacific Islander, and 9.33% identified as Hispanic or Latino. 

```{r whole-sample-demographics}
# Age M = 36.07, SD = 15.34 
# (note that the statistics for age in this open access data file are slightly different from the original ages after we changed all participants whose ages were > 89 into 90 due to HIPPA rules) 
round(mean(s2.outcomes$age, na.rm = T), 2)
round(sd(s2.outcomes$age, na.rm = T), 2)

# Gender
round(nrow(s2.outcomes[s2.outcomes$gender == "female",])/nrow(s2.outcomes)*100, 2)      # Female: 53.80%
round(nrow(s2.outcomes[s2.outcomes$gender == "genderqueer",])/nrow(s2.outcomes)*100, 2) # Queer: 3.86%
round(nrow(s2.outcomes[s2.outcomes$gender == "male",])/nrow(s2.outcomes)*100,2)         # Male: 42.34%

# Race
s2.outcomes %>%
  summarise(
    pct_white = round(100 * sum(white, na.rm = T)/sum(!is.na(race)),2),
    pct_asian = round(100 * sum(asian, na.rm = T)/sum(!is.na(race)),2),
    pct_black = round(100 * sum(black, na.rm = T)/sum(!is.na(race)),2),
    pct_native = round(100 * sum(native, na.rm = T)/sum(!is.na(race)),2),
    pct_islander = round(100 * sum(islander, na.rm = T)/sum(!is.na(race)),2),
    # total n identified as latino divided by total n that reported latino status
    pct_latino = round(100 * sum(latino, na.rm = T)/sum(!is.na(latino)),2)
    )

# Years of education M = 15.16, SD = 2.19
round(mean(s2.outcomes$yrs.education, na.rm = T), 2)
round(sd(s2.outcomes$yrs.education, na.rm = T), 2)
```


## 2.2 Descriptives of Outcome Variables

Across the sample, we observed threat facilitation RT scores differed from zero for all participants (M = -9.57, SD = 53.85, t(1839) = -7.63, p < .001) as well as high anxious participants as defined by GAD-7 (M = -16.90, SD = 45.89, t(253) = -5.87, p < .001) and the top quartile of the BHS (M = -13.55, SD = 48.59, t(454) = -5.95, p < .001).

We noted when conducting these analyses that our top quartile had significantly lower self-reported hypervigilance than the sample from Smith et al., 2019.  Thus, we additionally looked at participants in the top decile of BHS scores which yielded a sample with comparable hypervigilance levels to that reported in Smith et al (2019). For the top decile of BHS scores, threat facilitation scores also differed from zero (M = -15.20, SD = 50.43, t(167) = -3.91, p < .001). 

```{r outcome-descriptives}
# Mean TF RT score
t.test(s2.outcomes$TC.TIC.rt)        # M = -9.57 *** t = -7.6267, df = 1839
round(sd(s2.outcomes$TC.TIC.rt), 2)  # SD = 53.85

# Mean TF RT score for the SEVERE GAD group
t.test(s2.outcomes.gad.SEVERE$TC.TIC.rt)        # M = -16.90 *** t = -5.8675, df = 253
round(sd(s2.outcomes.gad.SEVERE$TC.TIC.rt), 2)  # SD = 45.89

# Mean TF RT score for the top QUARTILE BHS group
t.test(s2.outcomes.bhs.topQuartile$TC.TIC.rt)        # M = -13.55 *** t = -5.949, df = 454
round(sd(s2.outcomes.bhs.topQuartile$TC.TIC.rt), 2)  # SD = 48.59

# Mean TF RT score for the top DECILE BHS group
t.test(s2.outcomes.bhs.topDecile$TC.TIC.rt)        # M = -15.20 *** t = -3.9075, df = 167
round(sd(s2.outcomes.bhs.topDecile$TC.TIC.rt), 2)  # SD = 50.43
```


# 3. Descriptives and Demogrphics for Each Version

This produces the columns included in Table S3 (in the supplement) in the paper, and more columns on the confidence intervals of split half Pearson and Spearman correlations. 
```{r version-demographics}
s2.v.descriptives <- s2.outcomes %>% 
  mutate(
    female = ifelse(gender == "female", 1, 0),
    male = ifelse(gender == "male", 1, 0),
    queer = ifelse(gender == "genderqueer", 1, 0)
    ) %>%
  group_by(test_id) %>% 
  summarise(
    N = n(),
    medRTc = round(mean(all_medRTc)),
    accuracy = round(mean(all_accuracy), 2),
    TC = round(mean(TC_medRTc)),
    TIC = round(mean(TIC_medRTc)),
    TT = round(mean(TT_medRTc)),
    NN = round(mean(NN_medRTc)),
    TC.TIC.rt = round(mean(TC.TIC.rt)),
    TC.TT.rt = round(mean(TC.TT.rt)),
    TC.NN.rt = round(mean(TC.NN.rt)),
    Age = round(mean(age, na.rm = T)),
    pct_female = round(sum(female)/N*100),
    pct_male = round(sum(male)/N*100),
    pct_queer = round(sum(queer)/N*100),
    # total n identified as white divided by total reported race
    pct_white = round(100 * sum(white, na.rm = T)/sum(!is.na(race))),
    pct_asian = round(100 * sum(asian, na.rm = T)/sum(!is.na(race))),
    pct_black = round(100 * sum(black, na.rm = T)/sum(!is.na(race))),
    pct_native = round(100 * sum(native, na.rm = T)/sum(!is.na(race))),
    pct_islander = round(100 * sum(islander, na.rm = T)/sum(!is.na(race))),
    # total n identified as latino divided by total reported latino status
    pct_latino = round(100 * sum(latino, na.rm = T)/sum(!is.na(latino))),
    education = round(mean(yrs.education, na.rm = T))
    ) %>%
  merge(s2.rt.pearson, by = "test_id") %>%
  merge(s2.rt.spearman, by = "test_id") %>%
  merge(s2.acc.pearson, by = "test_id") %>%
  merge(s2.acc.spearman, by = "test_id")
```


# 4. Split-half Correlation by Anxiety Level

When we looked at split-half correlation of RT-based threat facilitation scores across anxiety levels, we did not see any evidence for higher correlation in high anxiety participants based on generalized anxiety or hypervigilance scores in the top quartile (all negative correlations that are likely due to chance and not interpretable: whole sample: rP(1838) = -.11; high generalized anxiety: rP(252) = -.3; top quartile of hypervigilance: rP(453) = -.002). 

We did, however, find significant split-half correlations for participants in the top decile of hypervigilance scores (rP(166) = .17, ρ = .29, 95% CI = .04-.48,  p < .05), though this split-half correlation was no longer different from zero when we used a nonparametric approach (rS(166) = .03, ρ = .06, 95% CI = .00-.35, p = .67). 

```{r correlation-anxiety-levels}
# Split-half Pearson correlation 

# Whole sample
cor.test(s2.half.stats$TC.TIC.1.rt, s2.half.stats$TC.TIC.2.rt) # r = -0.11 *** t = -4.61, df = 1838 CI: [-0.152, -0.061]
# Severe GAD
cor.test(s2.half.gad.SEVERE$TC.TIC.1.rt, s2.half.gad.SEVERE$TC.TIC.2.rt) # r = -0.31 *** t = -5.19, df = 252  CI: [-0.418, -0.195]
# Top Quartile BHS
cor.test(s2.half.bhs.topQuartile$TC.TIC.1.rt, s2.half.bhs.topQuartile$TC.TIC.2.rt) # r = -0.002, ns, t = -0.04, df = 453, CI: [-0.094,  0.090]
# Top Decile BHS
cor.test(s2.half.bhs.topDecile$TC.TIC.1.rt, s2.half.bhs.topDecile$TC.TIC.2.rt) # r = .17 *, t = 2.25, df = 166, CI: [0.021, 0.316]

# Split-half Spearman correlation - Top Decile BHS
cor.test(s2.half.bhs.topDecile$TC.TIC.1.rt, s2.half.bhs.topDecile$TC.TIC.2.rt, method = "spearman") # r = .17 *, t = 2.25, df = 166, CI: [0.021, 0.316]
spearmanCI(s2.half.bhs.topDecile$TC.TIC.1.rt,
           s2.half.bhs.topDecile$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # r = .033, CI [-0.14, 0.21]
```


# 5. Split-half Correlation for Top Decile of BHS

For the sample where overall correlation was significantly nonzero (top decile of BHS), we then looked at the split-half correlation of RT-based threat facilitation scores across all eight task versions within this group. In two of eight versions, split-half correlation was significantly different from zero. One version had horizontally-oriented faces as stimuli with 900 ms SOA (rP(22) = .73, ρ = .84, 95% CI = .64-.93, p <.001, version 12). The second version had horizontally-oriented scenes as stimuli with 500 ms SOA (rP(26) = .42, ρ = .59, 95% CI = .12-.82, p < .05, version 14).

```{r correlation-topDecileBHS}
# ---- PEARSON -----
# Split half PEARSON Correlation of threat facilitation RT scores, by version, among those within the top decile of BHS
s2.bhs.topDecile.rt.pearson <- s2.half.bhs.topDecile %>%
  group_by(test_id) %>%
  summarise(
    n.rt.pearson = n(),
    r.rt.pearson = cor(TC.TIC.1.rt, TC.TIC.2.rt),
    r.rt.pearson.lower = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[1], 2),
    r.rt.pearson.upper = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[2], 2),
    rho.rt.pearson = ifelse(r.rt.pearson > 0, (2*r.rt.pearson)/(1+r.rt.pearson), 0), 
    rho.rt.pearson.lower = round(ifelse(r.rt.pearson.lower > 0, (2*r.rt.pearson.lower)/(1+r.rt.pearson.lower), 0), 2),
    rho.rt.pearson.upper = round(ifelse(r.rt.pearson.upper > 0, (2*r.rt.pearson.upper)/(1+r.rt.pearson.upper), 0), 2),
    p.rt.pearson = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$p.value, 4),
    p.rt.pearson.star = ifelse(p.rt.pearson < .001, "***",
                        ifelse(p.rt.pearson < .01, "** ",
                        ifelse(p.rt.pearson < .05, "*  ", "   "))))
```


# 6. Split-half Correlation of Version 11

Finally, we looked at split-half correlations among anxious participants for the version of the emotional dot probe task that showed nonzero split-half correlation in both Study 1 and Study 2, including when using Spearman rank order correlations to estimate reliability. 

This version did not show a significant split-half correlation among participants with high generalized anxiety symptoms (rP(35) = .18, ρ = .31, 95% CI = .00-.64, p = .29) or the top decile of BHS scores (rP(21) = .28, ρ = .44, 95% CI = .00-.77, p = .19). 

Split-half correlations were significant among participants in the top quartile of BHS scores (rP(53) = .42, ρ = .59, 95% CI = .29-.76, p < .01), although this was no longer significant when using Spearman correlations (rS(53) = .19, ρ = .32, 95% CI = .00-.66, p = .16). 

```{r version-11}
# Split half Pearson correlation among people with severe GAD, in version 11 
s2.half.v11.gad7.SEVERE <- s2.half.gad.SEVERE %>%
  filter(test_id == 11) %>%
  summarise(    
    n.rt.pearson = n(),
    r.rt.pearson = cor(TC.TIC.1.rt, TC.TIC.2.rt),
    r.rt.pearson.lower = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[1], 2),
    r.rt.pearson.upper = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[2], 2),
    rho.rt.pearson = ifelse(r.rt.pearson > 0, (2*r.rt.pearson)/(1+r.rt.pearson), 0), 
    rho.rt.pearson.lower = round(ifelse(r.rt.pearson.lower > 0, (2*r.rt.pearson.lower)/(1+r.rt.pearson.lower), 0), 2),
    rho.rt.pearson.upper = round(ifelse(r.rt.pearson.upper > 0, (2*r.rt.pearson.upper)/(1+r.rt.pearson.upper), 0), 2),
    p.rt.pearson = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$p.value, 4),
    p.rt.pearson.star = ifelse(p.rt.pearson < .001, "***",
                        ifelse(p.rt.pearson < .01, "** ",
                        ifelse(p.rt.pearson < .05, "*  ", "   "))))

# Split half Pearson correlation among people with top quartile BHS, in version 11 
s2.half.v11.bhs.topQuartile <- s2.half.bhs.topQuartile %>%
  filter(test_id == 11) %>%
  summarise(    
    n.rt.pearson = n(),
    r.rt.pearson = cor(TC.TIC.1.rt, TC.TIC.2.rt),
    r.rt.pearson.lower = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[1], 2),
    r.rt.pearson.upper = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[2], 2),
    rho.rt.pearson = ifelse(r.rt.pearson > 0, (2*r.rt.pearson)/(1+r.rt.pearson), 0), 
    rho.rt.pearson.lower = round(ifelse(r.rt.pearson.lower > 0, (2*r.rt.pearson.lower)/(1+r.rt.pearson.lower), 0), 2),
    rho.rt.pearson.upper = round(ifelse(r.rt.pearson.upper > 0, (2*r.rt.pearson.upper)/(1+r.rt.pearson.upper), 0), 2),
    p.rt.pearson = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$p.value, 4),
    p.rt.pearson.star = ifelse(p.rt.pearson < .001, "***",
                        ifelse(p.rt.pearson < .01, "** ",
                        ifelse(p.rt.pearson < .05, "*  ", "   "))))
# Split half SPEARMAN correlation among people with top quartile BHS, in version 11 
spearmanCI(s2.half.bhs.topQuartile[s2.half.bhs.topQuartile$test_id == 11,]$TC.TIC.1.rt,
           s2.half.bhs.topQuartile[s2.half.bhs.topQuartile$test_id == 11,]$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # r = .19, CI [-0.11, 0.49]
cor.test(s2.half.bhs.topQuartile[s2.half.bhs.topQuartile$test_id == 11,]$TC.TIC.1.rt,
         s2.half.bhs.topQuartile[s2.half.bhs.topQuartile$test_id == 11,]$TC.TIC.2.rt, method = "spearman") # p = .167


# Split half correlation among people with top decile BHS, in version 11 
s2.half.v11.bhs.topDecile <- s2.half.bhs.topDecile %>%
  filter(test_id == 11) %>%
  summarise(    
    n.rt.pearson = n(),
    r.rt.pearson = cor(TC.TIC.1.rt, TC.TIC.2.rt),
    r.rt.pearson.lower = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[1], 2),
    r.rt.pearson.upper = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[2], 2),
    rho.rt.pearson = ifelse(r.rt.pearson > 0, (2*r.rt.pearson)/(1+r.rt.pearson), 0), 
    rho.rt.pearson.lower = round(ifelse(r.rt.pearson.lower > 0, (2*r.rt.pearson.lower)/(1+r.rt.pearson.lower), 0), 2),
    rho.rt.pearson.upper = round(ifelse(r.rt.pearson.upper > 0, (2*r.rt.pearson.upper)/(1+r.rt.pearson.upper), 0), 2),
    p.rt.pearson = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$p.value, 4),
    p.rt.pearson.star = ifelse(p.rt.pearson < .001, "***",
                        ifelse(p.rt.pearson < .01, "** ",
                        ifelse(p.rt.pearson < .05, "*  ", "   "))))
```


# 7. Plot Figure 4

## 7.1 Figure 4a GAD-7 Distribution

```{r gad-distribution}
# GAD7 Distribution
ggplot(s2.outcomes, aes(x = gad7, fill = gad7_2lvl)) +
  geom_histogram(alpha = 0.9, color = "white", aes(y = ..count../sum(..count..)), binwidth = 1, show.legend = FALSE) + 
  scale_fill_manual(values = c(colors[2], colors[1])) +
  scale_x_continuous(breaks = c(0,5,10,15,21), limits = c(-0.5, 21.5)) +
  scale_y_continuous(limits = c(0, 0.13), breaks = c(0, 0.05, 0.1), labels = c("0%", "5%", "10%")) +
  labs(title = "(a) Distribution of Generalized Anxiety Level", subtitle = "Whole Sample",
       x = "Generalized Anxiety Level", y = "Proportion of Participant") +
  geom_vline(xintercept = 4.5, linetype = 2) +
  geom_vline(xintercept = 9.5, linetype = 2) +
  geom_vline(xintercept = 14.5) +
  theme_bw() +
  annotate("text", x = 2, y = 0.12, label = "Minimal\nN = 672", size = 3.5) +
  annotate("text", x = 7, y = 0.12, label = "Mild\nN = 606", size = 3.5) +
  annotate("text", x = 12, y = 0.12, label = "Moderate\nN = 307", size = 3.5) +
  annotate("text", x = 18.5, y = 0.12, label = "Severe\nN = 254", size = 3.5)
# ggsave("figures/s2_figure_4a_GAD7_distribution.png", plot = last_plot(), width = 5.5, height=3.7)
```

## 7.2 Figure 4b BHS Distribution

```{r bhs-distribution}
# BHS Distribution
ggplot(s2.outcomes, aes(x = bhs, fill = bhs_4lvl_high)) +
  geom_histogram(alpha = 0.9, aes(y = ..count../sum(..count..)), color = "white", binwidth = 100/20, show.legend = FALSE) +
  scale_fill_manual(values = c(colors[2], colors[1])) +
  labs(title = "(b) Distribution of Hypervigilance Level", subtitle = "Whole Sample",
       x = "Hypervigilance Level", y = "Proportion of Participant") +
  scale_y_continuous(limits = c(0, 0.155),breaks = c(0, 0.05, 0.1, 0.15), labels = c("0%", "5%", "10%", "15%")) +
  scale_x_continuous(breaks = 0:10*10) +
  geom_vline(xintercept = 7.5, linetype = 2) +
  geom_vline(xintercept = 22.5, linetype = 2) +
  geom_vline(xintercept = 42.5) +
  theme_bw() +
  annotate("text", x = 0, y = 0.143, label = "1st\nQuartile\nN = 363", size = 3.3) +
  annotate("text", x = 15, y = 0.143, label = "2nd\nQuartile\nN=540", size = 3.3) +
  annotate("text", x = 32.5, y = 0.143, label = "3rd\nQuartile\nN = 481", size = 3.3) +
  annotate("text", x = 72, y = 0.143, label = "4th\nQuartile\nN = 455", size = 3.3) + 
  annotate("rect", xmin = 67.5, xmax = 102.5, ymin = 0, ymax=0.105, alpha = .2, fill = colors[1]) +
  annotate("text", x = 84, y = 0.085, label = "Top Decile\nN = 168", size = 3.3) 
# ggsave("figures/s2_figure_4b_BHS_distribution.png", plot = last_plot(), width = 5.5, height=3.7)
```

## 7.3 Figure 4c Violin 
```{r violin-plot}
combined <- rbind(s2.outcomes %>% filter(bhs_10lvl_high == "high") %>% mutate(group = "2.bhs.top.decile"),
                  s2.outcomes %>% filter(bhs_4lvl_high == "high") %>% mutate(group = "1.bhs.top.quartile"),
                  s2.outcomes %>% filter(gad7_2lvl == "high") %>% mutate(group = "0.high.gad7"))
ggplot(combined, aes(x = group, y = TC.TIC.rt, fill=group)) +  
  geom_violin(alpha = 0.6) +
  scale_fill_manual(values = c(colors[1], colors[2], colors[3])) +
  geom_boxplot(width = 0.1, outlier.size = .2, alpha = 0.6) +
  scale_x_discrete(labels = c('Severe \nGeneralized Anxiety', 'Top Quartile \nHypervigilance', 'Top Decile \nHypervigilance'), position = "bottom") +
  labs(title = "(c) Threat Facilitation RT Score", 
       subtitle = "By Group", 
       x = '', y = 'Threat Facilitation RT Score') + 
  theme_bw() +
  theme(legend.position = "none")
# ggsave("figures/s2_figure_4c_violin.png", plot = last_plot(), width=5.5, height = 3.9)
```

## 7.4 Figure 4d Split-half, severe GAD

```{r plot-rb-severeGAD}
# create a df for annotated text for plotting reliability for severe GAD7
s2.gad.SEVERE.pearson <- s2.half.gad.SEVERE %>%
  summarise(n = n(),
            r = cor(TC.TIC.1.rt, TC.TIC.2.rt),
            p = cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$p.value,
            p.star = ifelse(p < .001, "***",
                     ifelse(p < .01, "** ",
                     ifelse(p < .05, "*  ", "   "))))

# Plot reliability of TF RT Score with severe GAD7 
ggplot(s2.half.gad.SEVERE, aes(x = TC.TIC.1.rt, y = TC.TIC.2.rt)) +
  geom_point(alpha = 0.3, size = 2.8, color = colors[1]) + 
  geom_abline(slope = 0.67, size = 1, linetype = 2) +
  theme_bw() +
  scale_x_continuous(breaks = -6:6*100, expand = c(0,0)) +
  scale_y_continuous(breaks = -10:5*100, expand = c(0,0)) +
  coord_cartesian(ylim = c(-300, 300), xlim = c(-300, 300)) +
  geom_smooth(method = lm, color = colors[1]) +  
  geom_text(data = s2.gad.SEVERE.pearson, size = 4.5, color = colors[1],
            mapping = aes(x = 200,
                          y = 270,
                          label = paste0("r (", n-2, ") = ", round(r, 2)))) +
  labs(title = "(d) Split-half Correlation of Threat Facilitation RT Score", 
         subtitle = "Severe Generalized Anxiety Group",
         x = "Threat Facilitation RT Score on Odd Trials", y = "Threat Facilitation RT Score on Even Trials") +
  theme(plot.margin = margin(0.3,0.5,0.3,0.3, "cm"),
        plot.title = element_text(size = 12))
# ggsave("figures/s2_figure_4d_split-half_severeGAD.png", plot = last_plot(), width = 5, height = 5.2)
```

## 7.5 Figure 4e Split-half, top quartile BHS

```{r plot-rb-topQuartileBHS}
# create a df for annotated text for plotting reliability for top QUARTILE BHS
s2.bhs.topQuartile.pearson <- s2.half.bhs.topQuartile %>%
  summarise(n = n(),
            r = cor(TC.TIC.1.rt, TC.TIC.2.rt),
            p = cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$p.value,
            p.star = ifelse(p < .001, "***",
                     ifelse(p < .01, "** ",
                     ifelse(p < .05, "*  ", "   "))))

# Plot reliability of TF RT Score with top quartile BHS
ggplot(s2.half.bhs.topQuartile, aes(x = TC.TIC.1.rt, y = TC.TIC.2.rt)) +
  geom_point(alpha = 0.3, size = 2.8, color = colors[1]) + 
  geom_abline(slope = 0.67, size = 1, linetype = 2) +
  theme_bw() +
  scale_x_continuous(breaks = -5:5*100, expand = c(0,0)) +
  scale_y_continuous(breaks = -5:5*100, expand = c(0,0)) +
  coord_cartesian(ylim = c(-300, 300), xlim = c(-300, 300)) +
  stat_smooth(method = lm, color = colors[1]) +  
  geom_text(data = s2.bhs.topQuartile.pearson, size = 4.5, color = colors[1],
            mapping = aes(x = 200,
                          y = 270,
                          label = paste0("r (", n-2, ") = ", format(round(r, 2), nsmall = 2)))) +
    labs(title = "(e) Split-half Correlation of Threat Facilitation RT Score", 
         subtitle = "Top Quartile Hypervigilance Group", 
         x = "Threat Facilitation RT Score on Odd Trials", y = "Threat Facilitation RT Score on Even Trials") +
  theme(plot.margin = margin(0.3,0.5,0.3,0.3, "cm"),
        plot.title = element_text(size = 12))
# ggsave("figures/s2_figure_4e_split-half_topQuartileBHS.png", plot = last_plot(), width = 5, height = 5.2)
```

## 7.6 Figure 4f Split-half, top decile BHS

```{r plot-rb-topDecileBHS}
# create a df for annotated text for plotting reliability for top DECILE BHS
s2.bhs.topDecile.pearson <- s2.half.bhs.topDecile %>%
  summarise(n = n(),
            r = cor(TC.TIC.1.rt, TC.TIC.2.rt),
            p = cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$p.value,
            p.star = ifelse(p < .001, "***",
                     ifelse(p < .01, "** ",
                     ifelse(p < .05, "*  ", "   "))))

# Plot reliability of TF RT Score with top DECILE BHS - IN USE
ggplot(s2.half.bhs.topDecile, aes(x = TC.TIC.1.rt, y = TC.TIC.2.rt)) +
  geom_point(alpha = 0.3, size = 2.8, color = colors[1]) + 
  geom_abline(slope = 0.67, size = 1, linetype = 2) +
  theme_bw() +
  scale_x_continuous(breaks = -5:5*100, limits = c(-300, 300), expand = c(0,0)) +
  scale_y_continuous(breaks = -5:5*100, limits = c(-300, 300), expand = c(0,0)) +
  stat_smooth(method = lm, fullrange= TRUE, color = colors[1]) +  
  geom_text(data = s2.bhs.topDecile.pearson, size = 4.5, color = colors[1],
            mapping = aes(x = 200,
                          y = 270,
                          label = paste0("r (", n-2, ") = ", round(r, 2)))) +
    labs(title = "(f) Split-half Correlation of Threat Facilitation RT Score", 
         subtitle = "Top Decile Hypervigilance Group", 
         x = "Threat Facilitation RT Score on Odd Trials", y = "Threat Facilitation RT Score on Even Trials") +
  theme(plot.margin = margin(0.3,0.5,0.3,0.3, "cm"),
        plot.title = element_text(size = 12))
# ggsave("figures/s2_figure_4f_split-half_topDecileBHS.png", plot = last_plot(), width = 5, height = 5.2)
```

