---
title: "Reliability of the Emotional Dot Probe Task in Study 1"
---

**STUDY 1: The goal of this file is to analyze the reliability of the 36 digital versions of the Threat Dot Probe Task administered in Study 1. **    

```{r set-up, include = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)
library(ggpmisc)
library(spearmanCI)
# define colors we use for visualization
colors <- c("#0C7BDC", "coral", "deepskyblue3")

# Load processed data
# naming convention: s1 - study 1
# Outcome/person level data (one row per participant)
s1.all.outcomes <- read_csv("data/study1/openData_study1_outcomes_032523.csv")
# Trial level data (48 rows per participant) -> to calculate split half correlation and reliability
s1.all.trials <- read_csv("data/study1/openData_study1_trials_032523.csv")
```


# 1. Quality Control
After excluding participants that failed data quality control filters (N = 34 with accuracy < 60% or median RTc < 300 ms, Germine et al., 2022), the total sample was 7760 with between 176 to 276 participants completing each version.

```{r quality-control}
# Exclude participants with medRTc < 300 ms or accuracy < 60%
s1.outcomes <- s1.all.outcomes %>%
  filter(all_accuracy >= 0.6 & all_medRTc >= 300)
s1.excluded.id <- s1.all.outcomes[s1.all.outcomes$all_accuracy < 0.6 | s1.all.outcomes$all_medRTc < 300,]$id

# Total N included in analysis = 7760
nrow(s1.outcomes) 
# N excluded = 34
nrow(s1.all.outcomes) - nrow(s1.outcomes)

# Minimum and maximum N for each test version, test_id 6: N = 176, test_id 11: N = 276
s1.outcomes %>% 
  group_by(test_id) %>% 
  summarise(n = n()) %>% 
  arrange(n) %>%
  filter(row_number() == 1 | row_number() == n())
```


```{r process-trial-data, include = FALSE}
# condition 1: Threat congruent trials
# condition 2: Threat incongruent trials
# condition 3: Both threat trials
# condition 4: Both neutral trials
s1.parsed.trials <- s1.all.trials %>%
  # exclude participants who failed quality control criteria
  filter(!(id %in% s1.excluded.id) & condition != "practice") %>%
  mutate(rt = as.numeric(rt),
         correct = as.numeric(correct)) %>%
  group_by(id) %>%
  mutate(
    # number the trials (mixed among all conditions) 
    trial.all.cond = row_number(), 
    # label whether each trial is an odd (1) or even (2) trial (mixed among all conditions)
    half.all.cond = ifelse(trial.all.cond %% 2 == 1, 1, 2)) %>%
  group_by(id, condition) %>%
  mutate(
    # number the trials (within each condition)
    trial.by.cond = row_number(),
    # label whether each trial is an odd (1) or even (2) trial (within each condition)
    half.by.cond = ifelse(trial.by.cond %% 2 == 1, 1, 2))
  
# Calculate MEDIAN RT for odd and even trials (mixed among all conditions)
s1.half.med.rt.all.cond <- s1.parsed.trials %>%
  group_by(id, half.all.cond) %>%
  summarise(half.med.rt.all = median(rt)) %>%
  pivot_wider(names_from = half.all.cond, names_glue = "half.{half.all.cond}.rt", values_from = half.med.rt.all)

# Calculate MEAN accuracy for odd and even trials (mixed among all conditions)
s1.half.mean.acc.all.cond <- s1.parsed.trials %>%
  group_by(id, half.all.cond) %>%
  summarise(half.mean.acc.all = mean(correct)) %>%
  pivot_wider(names_from = half.all.cond, names_glue = "half.{half.all.cond}.acc", values_from = half.mean.acc.all)

s1.half.rt.acc.all.cond <- merge(s1.half.med.rt.all.cond, s1.half.mean.acc.all.cond, by = "id")

# Calculate MEDIAN RT for odd and even trials (within each condition)
s1.half.med.rt.by.cond <- s1.parsed.trials %>%
  group_by(id, condition, half.by.cond) %>%
  summarise(half.med.rt.by.cond = median(rt)) %>%
  pivot_wider(names_from = c(condition, half.by.cond), 
              names_glue = "cond{condition}.{half.by.cond}.rt", 
              values_from = half.med.rt.by.cond) %>%
  # Calculate the differences in median RT
  mutate(TC.TIC.1.rt = cond1.1.rt - cond2.1.rt,
         TC.TIC.2.rt = cond1.2.rt - cond2.2.rt,
         TC.TT.1.rt = cond1.1.rt - cond3.1.rt,
         TC.TT.2.rt = cond1.2.rt - cond3.2.rt,
         TC.NN.1.rt = cond1.1.rt - cond4.1.rt,
         TC.NN.2.rt = cond1.2.rt - cond4.2.rt)

# Calculate MEAN accuracy for odd and even trials (within each condition)
s1.half.mean.acc.by.cond <- s1.parsed.trials %>%
  group_by(id, condition, half.by.cond) %>%
  summarise(half.mean.rt.by.cond = mean(correct)) %>%
  pivot_wider(names_from = c(condition, half.by.cond), 
              names_glue = "cond{condition}.{half.by.cond}.acc", 
              values_from = half.mean.rt.by.cond) %>%
  # Calculate the differences in mean accuracy
  mutate(TC.TIC.1.acc = cond1.1.acc - cond2.1.acc,
         TC.TIC.2.acc = cond1.2.acc - cond2.2.acc,
         TC.TT.1.acc = cond1.1.acc - cond3.1.acc,
         TC.TT.2.acc = cond1.2.acc - cond3.2.acc,
         TC.NN.1.acc = cond1.1.acc - cond4.1.acc,
         TC.NN.2.acc = cond1.2.acc - cond4.2.acc)

s1.half.rt.acc.by.cond <- merge(s1.half.med.rt.by.cond, s1.half.mean.acc.by.cond, by = "id")

# Merge them into 1 df for convenience
s1.half.stats <- merge(s1.half.rt.acc.all.cond, s1.half.rt.acc.by.cond, by = "id")

s1.pt.info <- s1.outcomes %>% select(id, test_id, soa, imageType, orient, cond_num)
s1.half.stats <- merge(s1.pt.info, s1.half.stats, by = "id")
```


```{r version-parameters}
s1.v.params <- s1.outcomes %>%
  group_by(test_id) %>%
  filter(row_number() == 1) %>%
  select(test_id, soa, imageType, orient, cond_num)
```



```{r correlation-by-version}
# Split half PEARSON Correlation of threat facilitation RT scores, by version
s1.rt.pearson <- s1.half.stats %>%
  group_by(test_id) %>%
  summarise(
    n.rt.pearson = n(),
    r.rt.pearson = cor(TC.TIC.1.rt, TC.TIC.2.rt),
    r.rt.pearson.lower = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[1], 2),
    r.rt.pearson.upper = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$conf.int[2], 2),
    rho.rt.pearson = ifelse(r.rt.pearson > 0, (2*r.rt.pearson)/(1+r.rt.pearson), 0), 
    rho.rt.pearson.lower = round(ifelse(r.rt.pearson.lower > 0, (2*r.rt.pearson.lower)/(1+r.rt.pearson.lower), 0), 2),
    rho.rt.pearson.upper = round(ifelse(r.rt.pearson.upper > 0, (2*r.rt.pearson.upper)/(1+r.rt.pearson.upper), 0), 2),
    p.rt.pearson = round(cor.test(TC.TIC.1.rt, TC.TIC.2.rt)$p.value, 4),
    p.rt.pearson.star = ifelse(p.rt.pearson < .001, "***",
                        ifelse(p.rt.pearson < .01, "** ",
                        ifelse(p.rt.pearson < .05, "*  ", "   "))))

# Split half PEARSON Correlation of threat facilitation ACCURACY scores, by version
s1.acc.pearson <- s1.half.stats %>%
  group_by(test_id) %>%
  summarise(
    n.acc.pearson = n(),
    r.acc.pearson = round(cor(TC.TIC.1.acc, TC.TIC.2.acc), 2),
    r.acc.pearson.lower = round(cor.test(TC.TIC.1.acc, TC.TIC.2.acc)$conf.int[1], 2),
    r.acc.pearson.upper = round(cor.test(TC.TIC.1.acc, TC.TIC.2.acc)$conf.int[2], 2),
    rho.acc.pearson = round(ifelse(r.acc.pearson > 0, (2*r.acc.pearson)/(1+r.acc.pearson), 0), 2),
    rho.acc.pearson.lower = round(ifelse(r.acc.pearson.lower > 0, (2*r.acc.pearson.lower)/(1+r.acc.pearson.lower), 0), 2),
    rho.acc.pearson.upper = round(ifelse(r.acc.pearson.upper > 0, (2*r.acc.pearson.upper)/(1+r.acc.pearson.upper), 0), 2),
    p.acc.pearson = round(cor.test(TC.TIC.1.acc, TC.TIC.2.acc)$p.value, 4),
    p.acc.pearson.star = ifelse(p.acc.pearson < .001, "***",
                         ifelse(p.acc.pearson < .01, "** ",
                         ifelse(p.acc.pearson < .05, "*  ", "   "))))

# Split half SPEARMAN Correlation of threat facilitation RT scores, for versions with sig Pearson correlation
s1.rt.sig.test_ids <- s1.rt.pearson[s1.rt.pearson$p.rt.pearson < .05 & s1.rt.pearson$r.rt.pearson > 0,]$test_id
s1.rt.spearman <- data.frame(
  test_id = 1:36,
  r.rt.spearman = NA, 
  r.rt.spearman.lower = NA, 
  r.rt.spearman.upper = NA,
  p.rt.spearman = NA
)
for (i in s1.rt.sig.test_ids) {
  s1.rt.spearman[i, 2] <- round(cor.test(s1.half.stats[s1.half.stats$test_id == i,]$TC.TIC.1.rt,
                s1.half.stats[s1.half.stats$test_id == i,]$TC.TIC.2.rt, method = "spearman")$estimate, 2)
  s1.rt.spearman[i, 5] <- round(cor.test(s1.half.stats[s1.half.stats$test_id == i,]$TC.TIC.1.rt,
                s1.half.stats[s1.half.stats$test_id == i,]$TC.TIC.2.rt, method = "spearman")$p.value, 4)
}

# Split half SPEARMAN Correlation of threat facilitation ACCURACY scores, for versions with sig Pearson correlation
s1.acc.sig.test_ids <- s1.acc.pearson[s1.acc.pearson$p.acc.pearson < .05 & s1.acc.pearson$r.acc.pearson > 0,]$test_id
s1.acc.spearman <- data.frame(
  test_id = 1:36,
  r.acc.spearman = NA,
  r.acc.spearman.lower = NA, 
  r.acc.spearman.upper = NA,
  p.acc.spearman = NA
)
for (i in s1.acc.sig.test_ids) {
  s1.acc.spearman[i, 2] <- round(cor.test(s1.half.stats[s1.half.stats$test_id == i,]$TC.TIC.1.acc,
                s1.half.stats[s1.half.stats$test_id == i,]$TC.TIC.2.acc, method = "spearman")$estimate, 2)
  s1.acc.spearman[i, 5] <- round(cor.test(s1.half.stats[s1.half.stats$test_id == i,]$TC.TIC.1.acc,
                s1.half.stats[s1.half.stats$test_id == i,]$TC.TIC.2.acc, method = "spearman")$p.value, 4)
}

# Split half SPEARMAN RT CI 
# don't know how to store the outcome of spearmanCI into a table. So I'm manually adding them to the spearman table
# spearmanCI(s1.half.stats[s1.half.stats$test_id == 1,]$TC.TIC.1.rt, 
#            s1.half.stats[s1.half.stats$test_id == 1,]$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # rho's CI [-0.003, 0.300]
# spearmanCI(s1.half.stats[s1.half.stats$test_id == 10,]$TC.TIC.1.rt, 
#            s1.half.stats[s1.half.stats$test_id == 10,]$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # rho's CI [0.024, 0.307]
# spearmanCI(s1.half.stats[s1.half.stats$test_id == 14,]$TC.TIC.1.rt, 
#            s1.half.stats[s1.half.stats$test_id == 14,]$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # rho's CI [0.002, 0.277]
# spearmanCI(s1.half.stats[s1.half.stats$test_id == 15,]$TC.TIC.1.rt, 
#            s1.half.stats[s1.half.stats$test_id == 15,]$TC.TIC.2.rt, level = 0.95, method = "Euclidean", plot = FALSE) # rho's CI [0.031, 0.332]
s1.rt.spearman[1, 3] <- -.003
s1.rt.spearman[1, 4] <- .300
s1.rt.spearman[10, 3] <- .024
s1.rt.spearman[10, 4] <- .307
s1.rt.spearman[14, 3] <- .002
s1.rt.spearman[14, 4] <- .277
s1.rt.spearman[15, 3] <- .031
s1.rt.spearman[15, 4] <- .332
# Calculate rho's CI for the Spearman correlation of TF RT scores
s1.rt.spearman <- s1.rt.spearman %>%
  mutate(
    rho.rt.spearman = round(ifelse(r.rt.spearman > 0, (2*r.rt.spearman)/(1+r.rt.spearman), 0), 2),
    rho.rt.spearman.lower = round(ifelse(r.rt.spearman.lower > 0, (2*r.rt.spearman.lower)/(1+r.rt.spearman.lower), 0), 2),
    rho.rt.spearman.upper = round(ifelse(r.rt.spearman.upper > 0, (2*r.rt.spearman.upper)/(1+r.rt.spearman.upper), 0), 2),
  )

# Split half SPEARMAN Accuracy CI 
# spearmanCI(s1.half.stats[s1.half.stats$test_id == 11,]$TC.TIC.1.acc, 
#            s1.half.stats[s1.half.stats$test_id == 11,]$TC.TIC.2.acc, level = 0.95, method = "Euclidean", plot = FALSE) # r's CI [-0.029, 0.278]
# spearmanCI(s1.half.stats[s1.half.stats$test_id == 13,]$TC.TIC.1.acc, 
#            s1.half.stats[s1.half.stats$test_id == 13,]$TC.TIC.2.acc, level = 0.95, method = "Euclidean", plot = FALSE) # r's CI [0.196, 0.532]
# spearmanCI(s1.half.stats[s1.half.stats$test_id == 16,]$TC.TIC.1.acc, 
#            s1.half.stats[s1.half.stats$test_id == 16,]$TC.TIC.2.acc, level = 0.95, method = "Euclidean", plot = FALSE) # r's CI [-0.006, 0.314]
# spearmanCI(s1.half.stats[s1.half.stats$test_id == 25,]$TC.TIC.1.acc, 
#            s1.half.stats[s1.half.stats$test_id == 25,]$TC.TIC.2.acc, level = 0.95, method = "Euclidean", plot = FALSE) # r's CI [0.027, 0.359]
s1.acc.spearman[11, 3] <- -0.029
s1.acc.spearman[11, 4] <- 0.278
s1.acc.spearman[13, 3] <- 0.196
s1.acc.spearman[13, 4] <- 0.532
s1.acc.spearman[16, 3] <- -0.006
s1.acc.spearman[16, 4] <- 0.314
s1.acc.spearman[25, 3] <- 0.027
s1.acc.spearman[25, 4] <- 0.359
# Calculate rho's CI for the Spearman correlation of TF accuracy scores
s1.acc.spearman <- s1.acc.spearman %>%
  mutate(
    rho.acc.spearman = round(ifelse(r.acc.spearman > 0, (2*r.acc.spearman)/(1+r.acc.spearman), 0), 2),
    rho.acc.spearman.lower = round(ifelse(r.acc.spearman.lower > 0, (2*r.acc.spearman.lower)/(1+r.acc.spearman.lower), 0), 2),
    rho.acc.spearman.upper = round(ifelse(r.acc.spearman.upper > 0, (2*r.acc.spearman.upper)/(1+r.acc.spearman.upper), 0), 2),
  )
```


# 2. Descriptives and Demographics for the Whole Sample

## 2.1 Demographics 

Across the whole sample, the average age was 33.14 (SD = 16.35); 45.79% of participants identified as female, 52.01% identified as male, and 2.3% identified as nonbinary or gender queer. Of the total sample, 64.34% identified as European or White, 28.94% identified as Asian, 6.1% identified as African or Black, 2.71% identified as American Indian or Alaska Native, 1.01% identified as Native Hawiian or Pacific Islander, and 8.67% identified as Hispanic or Latino.

```{r whole-sample-demographics}
# Age M = 33.14, SD = 16.35 
# (note that the statistics for age in this open access data file are slightly different from the original ages after we changed all participants whose ages were > 89 into 90 due to HIPPA rules) 
round(mean(s1.outcomes$age, na.rm = T), 2)
round(sd(s1.outcomes$age, na.rm = T), 2)

# Gender
round(nrow(s1.outcomes[s1.outcomes$gender == "female",])/nrow(s1.outcomes)*100, 2)      # Female: 45.76%
round(nrow(s1.outcomes[s1.outcomes$gender == "genderqueer",])/nrow(s1.outcomes)*100, 2) # Queer: 2.23%
round(nrow(s1.outcomes[s1.outcomes$gender == "male",])/nrow(s1.outcomes)*100,2)         # Male: 52.01%

# Race
s1.outcomes %>%
  summarise(
    pct_white = round(100 * sum(white, na.rm = T)/sum(!is.na(race)),2),
    pct_asian = round(100 * sum(asian, na.rm = T)/sum(!is.na(race)),2),
    pct_black = round(100 * sum(black, na.rm = T)/sum(!is.na(race)),2),
    pct_native = round(100 * sum(native, na.rm = T)/sum(!is.na(race)),2),
    pct_islander = round(100 * sum(islander, na.rm = T)/sum(!is.na(race)),2),
    # total n identified as latino divided by total n that reported latino status
    pct_latino = round(100 * sum(latino, na.rm = T)/sum(!is.na(latino)),2)
    )

# Years of education M = 14.81, SD = 2.29
round(mean(s1.outcomes$yrs.education, na.rm = T), 2)
round(sd(s1.outcomes$yrs.education, na.rm = T), 2)
```

## 2.2 Descriptives of Outcome Variables

Across the sample, the mean threat facilitation medRTc scores were -7.92 (SD = 71.78, t(7759) =  -9.71, p < 0.001) indicating that participants were slightly faster to respond when the target appeared in the location of a threat stimulus, although this effect was small in magnitude. When we looked at threat facilitation scores using accuracy instead of RT, we found that participants were slightly less accurate to respond to threat congruent than threat incongruent trials (M = .003, SD = .04, t(7759) = 6.73, p < .001), although this effect was again small. 

```{r outcome-descriptives}
# Mean TF RT score
t.test(s1.outcomes$TC.TIC.rt)        #  M = -7.92 *** t = -9.7138, df = 7759
round(sd(s1.outcomes$TC.TIC.rt), 2)  # SD = 71.78

# Mean TF Accuracy score
t.test(s1.outcomes$TC.TIC.acc)        # M = 0.003 *** t = 6.7274, df = 7759
round(sd(s1.outcomes$TC.TIC.acc), 2)  # SD = 0.04
```


# 3. Descriptives and Demogrphics for Each Version

This produces the columns included in Table S2 (in the supplement) in the paper, and more columns on the confidence intervals of split half Pearson and Spearman correlations. 
```{r version-demographics}
s1.v.descriptives <- s1.outcomes %>% 
  mutate(
    female = ifelse(gender == "female", 1, 0),
    male = ifelse(gender == "male", 1, 0),
    queer = ifelse(gender == "genderqueer", 1, 0)
    ) %>%
  group_by(test_id) %>% 
  summarise(
    N = n(),
    medRTc = round(mean(all_medRTc)),
    accuracy = round(mean(all_accuracy), 2),
    TC = round(mean(TC_medRTc)),
    TIC = round(mean(TIC_medRTc)),
    TT = round(mean(TT_medRTc)),
    NN = round(mean(NN_medRTc)),
    TC.TIC.rt = round(mean(TC.TIC.rt)),
    TC.TT.rt = round(mean(TC.TT.rt)),
    TC.NN.rt = round(mean(TC.NN.rt)),
    Age = round(mean(age, na.rm = T)),
    pct_female = round(sum(female)/N*100),
    pct_male = round(sum(male)/N*100),
    pct_queer = round(sum(queer)/N*100),
    # total n identified as white divided by total reported race
    pct_white = round(100 * sum(white, na.rm = T)/sum(!is.na(race))),
    pct_asian = round(100 * sum(asian, na.rm = T)/sum(!is.na(race))),
    pct_black = round(100 * sum(black, na.rm = T)/sum(!is.na(race))),
    pct_native = round(100 * sum(native, na.rm = T)/sum(!is.na(race))),
    pct_islander = round(100 * sum(islander, na.rm = T)/sum(!is.na(race))),
    # total n identified as latino divided by total reported latino status
    pct_latino = round(100 * sum(latino, na.rm = T)/sum(!is.na(latino))),
    education = round(mean(yrs.education, na.rm = T))
    ) %>%
  merge(s1.rt.pearson, by = "test_id") %>%
  merge(s1.rt.spearman, by = "test_id") %>%
  merge(s1.acc.pearson, by = "test_id") %>%
  merge(s1.acc.spearman, by = "test_id")
```


# 4. Figure 2
## Figure 2 & S4a
```{r figure-2-s4a}
s1.v.params.rt.pearson <- s1.v.params %>%
  merge(s1.rt.pearson, by = "test_id")

# Versions with 2 and 4 conditions are plotted in different figures to save space in paper
s1.half.stats.2.cond <- s1.half.stats %>%
  filter(cond_num == 2)
s1.half.stats.4.cond <- s1.half.stats %>%
  filter(cond_num == 4)

s1.cor.2.cond.rt <- s1.v.params.rt.pearson %>%
  filter(cond_num == 2) %>%
  group_by(orient, imageType, soa)
s1.cor.4.cond.rt <- s1.v.params.rt.pearson %>%
  filter(cond_num == 4) %>%
  group_by(orient, imageType, soa)

r.italic <- "italic(r[P])"
rho.italic <- "italic(\u03c1)"
# a function to remove the zero and period before decimals
fm <- function(val) { sub("^(-?)0.", "\\1.", sprintf("%.2f", val)) }


# Plot split-half correlation, facetted by version
rb.by.version.rt.18 <- function(half.stats.df, cor.df, var1, var2){
  min = -500
  max = 500
  text.x = 0
  text.y1 = 450
  text.y2 = 380
  s = 2
  ggplot(half.stats.df, aes(x = var1, y = var2, color = orient)) +
    geom_point(alpha = 0.2, size = s) + 
    geom_abline(slope = 0.67, size = 0.5, linetype = 2) +
    scale_x_continuous(expand = c(0, 0), breaks = c(-500, -300, -100, 100, 300, 500),
                       # add a label for facets
                       sec.axis = sec_axis(~ . , name = "Stimulus Type", breaks = NULL, labels = NULL)) +
    scale_y_continuous(expand = c(0, 0), breaks = c(-500, -300, -100, 100, 300, 500),
                       sec.axis = sec_axis(~ . , name = "Stimulus Onset Asynchrony", breaks = NULL, labels = NULL)) +
    scale_color_manual(values = c(colors[2], colors[3])) + 
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = -290,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0("v"),
                            color = orient)) +
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = -240,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0(test_id),
                            color = orient)) +
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = -147,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0(r.italic),
                            color = orient), parse = TRUE) +    
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = 50,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0("(", n.rt.pearson-2, ") = ", fm(r.rt.pearson), ","),
                            color = orient)) +    
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = 250,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0(rho.italic),
                            color = orient), parse = TRUE) +    
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = 350,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0(" = ", fm(rho.rt.pearson)),
                            color = orient)) +
    facet_grid(soa ~ imageType) +
    stat_smooth(method = "lm", fullrange = TRUE, se = F) +
    coord_cartesian(ylim = c(min, max), xlim = c(min, max)) +
    labs(x = "Odd trials", y = "Even trials", color = "Stimulus\nOrientation") + 
    theme_minimal() +
    theme(plot.title = element_text(family = "Times"), 
          panel.spacing = unit(1.3, "lines"),
          panel.border = element_rect(size = 0.5, color = "grey", fill = NA),
          axis.ticks = element_line(size = 0.3),
          strip.text.x = element_text(size = 11),
          strip.text.y = element_text(size = 11, vjust = 1.5),
          axis.title.y = element_text(vjust = 2)
          ) 
}


rb.by.version.rt.18(s1.half.stats.2.cond, s1.cor.2.cond.rt, 
                              s1.half.stats.2.cond$TC.TIC.1.rt,
                              s1.half.stats.2.cond$TC.TIC.2.rt)
# ggsave("figures/dotProbe_figure_2_s4a_p1.png", plot = last_plot(), width = 10, height = 8.7)


rb.by.version.rt.18(s1.half.stats.4.cond, s1.cor.4.cond.rt, 
                               s1.half.stats.4.cond$TC.TIC.1.rt,
                               s1.half.stats.4.cond$TC.TIC.2.rt)
# ggsave("figures/dotProbe_figure_s4a_p2.png", plot = last_plot(), width = 10, height = 8.7)
```

## Figure S4b
```{r figure-s4b}
s1.v.params.acc.pearson <- s1.v.params %>%
  merge(s1.acc.pearson, by = "test_id")

s1.cor.2.cond.acc <- s1.v.params.acc.pearson %>%
  filter(cond_num == 2) %>%
  group_by(orient, imageType, soa)
s1.cor.4.cond.acc <- s1.v.params.acc.pearson %>%
  filter(cond_num == 4) %>%
  group_by(orient, imageType, soa)


rb.by.version.acc.18 <- function(half.stats.df, cor.df, var1, var2, cond_num = 2){
  if(cond_num == 2)
  {
    min = -0.4
    max = 0.4
    text.y1 = 0.36
    text.y2 = 0.3
    text.x.v = -.23
    text.x.testid = -.19
    text.x.r = -.11
    text.x.rvalue = .05
    text.x.rho = .21
    text.x.rhovalue = .285
  }
  else {
    min = -0.6
    max = 0.6
    text.y1 = 0.54
    text.y2 = 0.45
    text.x.v = -.35
    text.x.testid = -.28
    text.x.r = -.16
    text.x.rvalue = .08
    text.x.rho = .32
    text.x.rhovalue = .44
  }
  s = 3
  ggplot(half.stats.df, aes(x = var1, y = var2, color = orient)) +
    geom_jitter(alpha = 0.2, size = s) + 
    geom_abline(slope = 0.67, size = 0.5, linetype = 2) +
    scale_x_continuous(expand = c(0, 0), breaks = c(-0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6), limits = c(min, max),
                       # add a label for facets
                       sec.axis = sec_axis(~ . , name = "Stimulus Type", breaks = NULL, labels = NULL)) +
    scale_y_continuous(expand = c(0, 0), breaks = c(-0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6), limits = c(min, max),
                       sec.axis = sec_axis(~ . , name = "Stimulus Onset Asynchrony", breaks = NULL, labels = NULL)) +
    scale_color_manual(values = c(colors[2], colors[3])) + 
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = text.x.v,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0("v"),
                            color = orient)) +
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = text.x.testid,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0(test_id),
                            color = orient)) +
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = text.x.r,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0(r.italic),
                            color = orient), parse = TRUE) +
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = text.x.rvalue,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0("(", n.acc.pearson-2, ") = ", fm(r.acc.pearson), ","),
                            color = orient)) +
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = text.x.rho,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0(rho.italic),
                            color = orient), parse = TRUE) +
    geom_text(data = cor.df, size = 3.7,
              mapping = aes(x = text.x.rhovalue,
                            y = c(text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1, text.y1,
                                  text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2, text.y2),
                            label = paste0(" = ", fm(rho.acc.pearson)),
                            color = orient)) +
    facet_grid(soa ~ imageType) +
    stat_smooth(method = "lm", fullrange = TRUE, se = F) +
    labs(x = "Odd trials", y = "Even trials", color = "Stimulus\nOrientation") + 
    theme_minimal() +
    theme(plot.title = element_text(family = "Times"), 
          panel.spacing = unit(1.3, "lines"),
          panel.border = element_rect(size = 0.5, color = "grey", fill = NA),
          axis.ticks = element_line(size = 0.3),
          strip.text.x = element_text(size = 11),
          strip.text.y = element_text(size = 11, vjust = 1.5),
          axis.title.y = element_text(vjust = 2)) 
}

rb.by.version.acc.18(s1.half.stats.2.cond, s1.cor.2.cond.acc,
                              s1.half.stats.2.cond$TC.TIC.1.acc,
                              s1.half.stats.2.cond$TC.TIC.2.acc, 2)
# ggsave("figures/dotProbe_figure_s4b_p1.png", plot = last_plot(), width = 10, height = 8.7)

rb.by.version.acc.18(s1.half.stats.4.cond, s1.cor.4.cond.acc,
                              s1.half.stats.4.cond$TC.TIC.1.acc,
                              s1.half.stats.4.cond$TC.TIC.2.acc, 4)
# ggsave("figures/dotProbe_figure_s4b_p2.png", plot = last_plot(), width = 10, height = 8.7)
```


# 5. Figure 3
## Fig 3a. Distribution of split-half Pearson correlation (RT)
```{r figure-3a}
ggplot(s1.rt.pearson, aes(x = r.rt.pearson)) +
  geom_histogram(alpha = 0.9, color = "white", fill = colors[1], binwidth = 0.05, show.legend = FALSE) +
  scale_x_continuous("Split-half Correlation", limits = c(-.7, .7), 
                     breaks = c(-7:6*0.1, 0.67), 
                     labels = c("-0.7", "-0.6", "-0.5", "-0.4", "-0.3", "-0.2", "-0.1", "0", "0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.67"),
                     expand = c(.001, .001)) +
  scale_y_continuous("Number of Version", limits = c(0, 7), breaks = 0:7, expand = c(0.004,0)) +
  geom_vline(xintercept = 0.67, linetype = 2) +
  theme_bw() +
  theme(plot.margin = margin(0.3,0.5,0.3,0.3, "cm"))
# ggsave("figures/s1_figure_3a.png", width = 6, height = 3.5, plot = last_plot())
```


## Figure 3b. Distribution of split-half Pearson correlation (accuracy)
```{r figure3b}
ggplot(s1.acc.pearson, aes(x = r.acc.pearson)) +
  geom_histogram(alpha = 0.9, color = "white", fill = colors[1], binwidth = 0.05, show.legend = FALSE) +
  scale_x_continuous("Split-half Correlation", 
                     limits = c(-.7, .7),
                     breaks = c(-7:6*0.1, 0.67),
                     labels = c("-0.7", "-0.6", "-0.5", "-0.4", "-0.3", "-0.2", "-0.1", "0", "0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.67"),
                     expand = c(.001, .001)) +
  scale_y_continuous("Number of Version", limits = c(0, 7), breaks = 0:7, expand = c(0.004,0)) +
  geom_vline(xintercept = 0.67, linetype = 2) +
  theme_bw() +
  theme(plot.margin = margin(0.3,0.5,0.3,0.3, "cm"))
ggsave("figures/s1_figure_3b.png", width = 6, height = 3.5, plot = last_plot())
```

